Papers

### 2023-01-05 quarto/index.qmd
update

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
	*"Adapters, prefix tuning, BitFit, LoRA, ... do design patterns exist?"*
	In *arXiv*, 2022<br>

* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, M. Li<br>
	<a href="https://arxiv.org/abs/2212.10929" target="_blank">
	SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
	*"If your prompt tuning can't converge easily, make it semi-parametric."*
	In *arXiv*, 2022<br>
	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

>>>>

* J. Chen, **A. Zhang**, X. Shi, M. Li, A. J. Smola, and D. Yang<br>
	<a href="https://d2l-webdata.s3.us-west-2.amazonaws.com/papers/PEFT-design-spaces.pdf" target="_blank">Parameter-Efficient Fine-Tuning Design Spaces</a><br>
	*"Don't assign the SAME parameter-efficient fine-tuning strategy to DIFFERENT layers."*
	In *arXiv*, 2022<br>

* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
	<a href="https://arxiv.org/abs/2212.10929" target="_blank">
	SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
	*"If your prompt tuning can't converge easily, make it semi-parametric."*
	In *arXiv*, 2022<br>
	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

### 2023-01-05 quarto/papers.qmd
update

## 2022

@@

* C. He, S. Zheng, **A. Zhang**, G. Karypis, T. Chilimbi, M. Soltanolkotabi, S. Avestimehr<br>
<a href="https://arxiv.org/abs/2212.05191" target="_blank">
SMILE: Scaling Mixture-of-Experts with Efficient Bi-level Routing</a><br>
*"2.5x speedup over Switch Transformers"*
In *arXiv*, 2022<br>

@@

@@

## 2021

@@

## 2020

@@

## 2019

@@

## Earlier

>>>>

@@

* Z. Liu, Z. Tang, X. Shi, **A. Zhang**, M. Li, A. Shrivastava, and A. Wilson<br>
<a href="https://arxiv.org/abs/2212.14453" target="_blank">Learning Multimodal Data Augmentation in Feature Space</a><br>
*"The first augmentation method to be applied to the joint of text, image, and tabular data."*
In *arXiv*, 2022<br>

@@

* C. He, S. Zheng, **A. Zhang**, G. Karypis, T. Chilimbi, M. Soltanolkotabi, and S. Avestimehr<br>
<a href="https://arxiv.org/abs/2212.05191" target="_blank">
SMILE: Scaling Mixture-of-Experts with Efficient Bi-level Routing</a><br>
*"2.5x speedup over Switch Transformers."*
In *arXiv*, 2022<br>

@@

@@

@@

@@
